|

### 2023-03-08 paper/paper.Rmd
some template updates
data and more sketches

---
title: |
  Introducing STRAIN: A simple and interpretable pass rush metric inspired by materials science
short_title: STRAIN
authors: 
- name: "Author 1"
  affiliation: "Address"
  city: "City"
  country: "Country"
  email: "email1\\@example.com"
- name: "Author 2"
  affiliation: "Address2"
  city: "City2"
  country: "Country2"
  email: "email2\\@example.com"
abstract: |
  Abstract goes here
keywords: tracking data, Bornn legacy
bibliography: "bibliography"
output: rticles::rss_article
---

@@

1. Introduction

@@

Tracking data, big data bowl
See @Baumer2023Big, @Macdonald2020Recreating, and @Kovalchik2023Player for more details

Importance of linemen. Did all hard work. QB

@@

2. Data

talk about data

3. Methods

4. Results

@@

5. Discussion

@@

@@

# Data

introduce data

@@

@@

* The distance between player $j$ and the quarterback at frame $t$ during play $i$ is $f_{d_{ij}}(t) = \sqrt{(x_{ijt} - x^{QB}_{it})^2 + (y_{ijt} - y^{QB}_{it})^2}$.
* The rate at which player $j$ is moving towards the quarterback at frame $t$ during play $i$ is $\displaystyle f'_{d_{ij}}(t) = \frac{df_{d_{ij}}(t)}{dt}$.
* The STRAIN for player $j$ at frame $t$ during play $i$ is

>>>>

---
title: |
  Introducing STRAIN: A simple and interpretable pass rush metric inspired by materials science
short_title: STRAIN
authors: 
- name: "Author 1"
  affiliation: "Address"
  city: "City"
  country: "Country"
  email: "email1\\@example.com"
- name: "Author 2"
  affiliation: "Address2"
  city: "City2"
  country: "Country2"
  email: "email2\\@example.com"
abstract: |
  Abstract goes here
keywords: tracking data, Bornn legacy, too much Canadian
bibliography: "bibliography"
output: rticles::rss_article
---

\newpage

@@

i. Introduction

@@

Tracking data in recent years, NFL

examples of past nfl tracking data projects

See @Baumer2023Big, @Macdonald2020Recreating, and @Kovalchik2023Player for more details

Importance of D-linemen, pass rush (Maybe talk about role of each position, edge vs interior, defensive formation)

@@

ii. Methods

a. data

2023 bdb [@bdb2023]

first 8 weeks 2021 season

tracking: locations of players and ball, 10 fps,

pre-processing standardize

PFF scouting: pass rush role

sample restriction: remove plays w multiple QB

frames between snap and QB outcome (pass forward, sack)

sample size

b. strain rate

c. applying to pass rush

iii. Results

@@

iv. Discussion

\newpage

@@

## Previous Metrics for Pass Rush Evaluation

## Our Contribution

@@

The remainder of this paper is outlined as follows.

@@

## Data

bdb

@@

* The distance between player $j$ and the quarterback at frame $t$ during play $i$ is

$$f_{d_{ij}}(t) = \sqrt{\left(x_{ijt} - x^{QB}_{it}\right)^2 + \left(y_{ijt} - y^{QB}_{it}\right)^2}$$.

* The rate at which player $j$ is moving towards the quarterback at frame $t$ during play $i$ is

$$\displaystyle f'_{d_{ij}}(t) = \frac{df_{d_{ij}}(t)}{dt}$$.

* The STRAIN for player $j$ at frame $t$ during play $i$ is
